MSOA Industrial Electricty and Gas maps

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Solved some of the errors

## Mapping Commercial
### Mapping Electricty
####2019
```{r Loading in the MSOA electricity consumption data for industry }
# electricity consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
msoa_elecDatanondom <- readr::read_csv(inFile)
head(msoa_elecDatanondom)
```

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Difference from 2010 to 2019
```{r Creating the mean electricty consumption from the industrial sector MOSA}
##BROKEN
ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2010.csv")
ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2019.csv")  
ndelec_msoa_2010$ndelec2010 <-ndelec_msoa_2010$' Mean consumption (kWh per meter)'                                       
ndelec_msoa_2019$ndelec2019 <-ndelec_msoa_2019$' Mean consumption (kWh per meter) '
merged_nondomelec <-merge(ndelec_msoa_2010, ndelec_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_ndelec)
merged_ndelec$ndelec_diff<-merged_ndelec$ndelec2019 - merged_ndelec$ndelec2010
summary(merged_ndelec)
```
```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
merged_nondomelec$MSOA11CD <- merged_nondomelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nondom20102019 <- merge(msoa_sf_data, merged_nondomelec) #merging these
ggplot2::ggplot(msoa_nondom20102019) +
  geom_sf(aes(fill=nondom_diff))+ 
  scale_fill_continuous(name="Change in  mean electricty consumption for the industrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```
### Mapping Gas
####2019
```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_NonDom_Gas_2019.csv")
msoa_gasDatanondom <- readr::read_csv(inFile)
head(msoa_gasDatanondom)
```

```{r Mapping the gas consumption of the MSOAs Industrial Sector}
msoa_gasDatanondom$MSOA11CD <- msoa_gasDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom_gas <-merge(msoa_sf_data, msoa_gasDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom_gas) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
> The holes tell you where there is no non-domestic gas use

####Mapping the difference in non domestic gas from 2010 to 2019 
```{r Creating the difference in non domestic gas consumption in the MSOA}
nondomgas_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NonDom_Gas_2010.csv"))
nondomgas_msoa_2019<-readr::read_csv(paste0(dataFolder,"energy/MSOA_NonDom_Gas_2019.csv"))
nondomgas_msoa_2010$nondomgas2010<-nondomgas_msoa_2010$' Mean consumption (kWh per meter)'
nondomgas_msoa_2019$nondomgas2019<-nondomgas_msoa_2019$' Mean consumption (kWh per meter)'
merged_nondomgas20102019<-merge(nondomgas_msoa_2010, nondomgas_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_nondomgas20102019)
merged_nondomgas20102019$nondomgas_diff<-merged_nondomgas20102019$nondomgas2019 - merged_nondomgas20102019$nondomgas2010 ##BROKEN
summary(merged_nondomgas20102019)
```

```{r Mapping the change in non domestic gas usage in the MSOA}
merged_nondomgas20102019$MSOA11CD <- merged_df$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_nondomgas20102019 <- merge(msoa_sf_data, merged_nondomgas20102019) #merging these
ggplot2::ggplot(msoa_nondomgas20102019) +
  geom_sf(aes(fill=pc_diff))+ 
  scale_fill_continuous(name="Change in mean gas consumption in the indistrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```

>>>>

## Mapping Commercial
### Mapping Electricty
####2019
```{r Loading in the MSOA electricity consumption data for industry }
# electricity consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv")
msoa_elecDatanondom <- readr::read_csv(inFile)
head(msoa_elecDatanondom)
```

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Difference from 2010 to 2019
```{r Creating the mean electricty consumption from the industrial sector MOSA}
ndelec_msoa_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2010.csv"))
ndelec_msoa_2019<-readr::read_csv(paste0(dataFolder,"/energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv"))
ndelec_msoa_2010$ndelec2010<-ndelec_msoa_2010$'Mean consumption (kWh per meter)'                                       
ndelec_msoa_2019$ndelec2019<-ndelec_msoa_2019$'Mean consumption (kWh per meter)'
merged_ndelec<-merge(ndelec_msoa_2010, ndelec_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_ndelec)
merged_ndelec$ndelec_diff<-(as.numeric(merged_ndelec$ndelec2019))-(as.numeric(merged_ndelec$ndelec2010))
summary(merged_ndelec)
```

```{r Creating the mean electricty consumption from the industrial sector MOSA}
ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2010.csv"))
ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv"))
ndelec_msoa_2010$ndelec2010 <-ndelec_msoa_2010$' Mean consumption (kWh per meter)'                                       
ndelec_msoa_2019$ndelec2019 <-ndelec_msoa_2019$' Mean consumption (kWh per meter) '
merged_nondomelec <-merge(ndelec_msoa_2010, ndelec_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_ndelec)
merged_ndelec$ndelec_diff<-as.numeric(merged_ndelec$ndelec2019) - as.numeric(merged_ndelec$ndelec2010) ##BROKEN
summary(merged_ndelec)
```
```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
ggplot2::ggplot(msoa_nd20102019) +
  geom_sf(aes(fill=" Mean consumption (kWh per meter)"))+ 
  scale_fill_continuous(name="Change in mean electricty consumption for the industrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```
### Mapping Gas
####2019
```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv")
msoa_ndgas <- readr::read_csv(inFile)
head(msoa_ndgas)
```

```{r Mapping the gas consumption of the MSOAs Industrial Sector}
msoa_ndgas$MSOA11CD <- msoa_ndgas$'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_ndgas <-merge(msoa_sf_data, msoa_ndgas)
ggplot2::ggplot(msoa_merged_ndgas) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
> The holes tell you where there is no non-domestic gas use

####Mapping the difference in non domestic gas from 2010 to 2019 
```{r Creating the difference in non domestic gas consumption in the MSOA}
msoa_2010_ndgas<-readr::read_csv(paste0(dataFolder,"/energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2010.csv"))
msoa_2019_ndgas<-readr::read_csv(paste0(dataFolder,"energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv"))
msoa_2010_ndgas$ndgas2010<-msoa_2010_ndgas$'Mean consumption (kWh per meter)'
msoa_2019_ndgas$ndgas2019<-msoa_2019_ndgas$'Mean consumption (kWh per meter)'

merged_ndgas20102019<-merge(msoa_2010_ndgas, msoa_2019_ndgas, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_ndgas20102019)
merged_ndgas20102019$ndgas_diff<-merged_ndgas20102019$nondomgas2019 - merged_nd20102019$nondomgas2010 ##BROKEN
summary(merged_nondomgas20102019)
```

```{r Mapping the change in non domestic gas usage in the MSOA}
merged_nondomgas20102019$MSOA11CD <- merged_df$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_nondomgas20102019 <- merge(msoa_sf_data, merged_nondomgas20102019) #merging these
ggplot2::ggplot(msoa_nondomgas20102019) +
  geom_sf(aes(fill=pc_diff))+ 
  scale_fill_continuous(name="Change in mean gas consumption in the indistrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
##BROKEN
```
